---
title: "Clustering"
author: "Ginevra Cocciardi"
output: pdf_document
---
```{r}
rm(list = ls())
setwd("/Users/ginevracocciardi/Desktop/tesi/dati")
campione <- read.csv('campione_cat.csv', sep = ';', dec = ",")
corrds <- read.csv('corrds.csv', sep = ',', dec = ",")
corrds$X.1 <- NULL
```

I add the variable concern which was only present as numeric:

```{r}

campione$concern_num <- rowSums( corrds[,3:5] )
campione$concern <- ''

for (i in (1:nrow(campione))) {
  if (campione$concern_num[i] <= 3){
    campione$concern[i] <- 'No'
  } else if (campione$concern_num[i] > 3 & campione$concern_num[i] <= 6) {
    campione$concern[i] <- 'Non molto'
  } else if (campione$concern_num[i] > 6 & campione$concern_num[i] <= 9) {
    campione$concern[i] <- 'Abbastanza'
  } else if (campione$concern_num[i] > 9) {
    campione$concern[i] <- 'Molto'
  }
} 

campione['concern'] <- factor(campione$concern, 
                                          levels = c('No', "Non molto", 'Abbastanza', 'Molto'), 
                                          ordered = TRUE)


data <- campione[, c(2, 29, 6:10, 12:13, 24, 27, 16, 17:23)]
```

##### CLUSTERING

Loading the libraries:

```{r}
library(dplyr)    # for data cleaning
library(cluster)  # for gower similarity and pam
library(Rtsne)    # for t-SNE plot
library(ggplot2)  # for visualization
```

I take away the variable "compri", whoch is our control variable:
```{r}
data_cluster <- data[, c(1:7, 9:19)]
```

Since we have mixed data we can't use Euclidean distance: we use Gower distance to compute the dissimilarity matrix.

```{r}
gower_dist <- daisy(data_cluster,
                    metric = "gower",
                    type = list(logratio = 3))
#summary(gower_dist)
gower_mat <- as.matrix(gower_dist)

# la coppia più uguale
# data[which(gower_mat == min(gower_mat[gower_mat != min(gower_mat)]), arr.ind = TRUE)[1, ], ]
# la coppia più diversa
# data[which(gower_mat == max(gower_mat[gower_mat != max(gower_mat)]), arr.ind = TRUE)[1, ], ]
```

Now we need to choose the number of clusters. The used metric is silhouette width. We check from 2 to 10:

```{r}
sil_width <- c(NA)
for(i in 2:10){
  
  pam_fit <- pam(gower_dist,
                 diss = TRUE,
                 k = i)
  
  sil_width[i] <- pam_fit$silinfo$avg.width
  
}
# Plot sihouette width (higher is better)
plot(1:10, sil_width,
     xlab = "Number of clusters",
     ylab = "Silhouette Width")
lines(1:10, sil_width)
```

Although 2 is the higher we go for three (second best):

```{r}
pam_fit <- pam(gower_dist, diss = TRUE, k = 3)
#pam_fit$clusinfo
```

Now we actually look into the clusters, adding also the variable "compri" to the dataset used for the clustering, so that we see how that has been divided:

```{r}
data_cluster$compri <- data$compri

pam_results <- data_cluster %>%
  mutate(cluster = pam_fit$clustering) %>%
  group_by(cluster) %>%
  do(the_summary = summary(.))
pam_results$the_summary
```

Now let's plot them:

```{r}
set.seed(10)
tsne_obj <- Rtsne(gower_dist, is_distance = TRUE) # riduzione dimensionalità per plot

tsne_data <- tsne_obj$Y %>%
  data.frame() %>%
  setNames(c("X", "Y")) %>%
  mutate(cluster = factor(pam_fit$clustering),
         name = data_cluster$compri)
ggplot(aes(x = X, y = Y), data = tsne_data) +
  geom_point(aes(color = cluster))

```


